Location and Scale-Invariant Power Transformations for Transforming Data to Normality

### 2023-11-16 manuscript/manuscript.Rmd
Further work.

@@

To assess whether the modified power transformations lead to $\lambda$ values that are invariant to location and scale of the distribution, we simulate three different distributions. The first distribution is a normal distribution, as previously shown in Figure \ref{fig:decreased-normality}.
We first randomly draw $10000$ values from a normal distribution: $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)$, or equivalently $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)$.
The second distribution is a right-skewed normal distribution $\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)$.
The third distribution is a left-skewed normal distribution $\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)$.
We then compute transformation parameter $\hat{\lambda}$ using the original definitions (equations \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}) and the location and scale invariant definitions (equations \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) for each distribution. To assess location invariance, a positive value $d_{\text{shift}}$ is added to each distribution with $d_{\text{shift}} \in [1, 10^6]$. Similarly, to assess scale invariance, each distribution is multiplied by a positive value $d_{\text{scale}}$, where $d_{\text{scale}} \in [1, 10^6]$.

```{r shifted-distributions, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Invariant power transformation produces transformation parameters that are invariant to location and shape. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively, which then underwent a shift $d_{\\text{shift}}$ or multiplication by $d_{\\text{scale}}$. ",
  "Estimates of transformation parameter $\\lambda$ with the conventional power transformations (circle) show strong dependency on the overall location and scale of the distribution, ",
  "whereas estimates with the invariant power transformations (triangle) are constant.")

@@

# Appendix A: Log-likelihood functions for invariant transformations.

Location and scale-invariant Box-Cox and Yeo-Johnson transformations are parameterised using location $x_0$ and scale $s$ parameters, in addition to transformation parameter $\lambda$.
This leads to the following transformations. The location and scale-invariant Box-Cox transformation is:

```{=latex}
\begin{equation}
\phi_{\text{BC}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left(\frac{x_i - x_0}{s} \right)^\lambda - 1 \right) / \lambda & \text{if } \lambda \neq 0\\
\log\left[\frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0
\end{cases}
\end{equation}
```
Where $x_i - x_0 > 0$.
The location and scale-invariant Yeo-Johnson transformation is:

```{=latex}
\begin{equation}
\phi_{\text{YJ}}^{\lambda, x_0, s} (x_i) = 
\begin{cases}
\left( \left( 1 + \frac{x_i - x_0}{s}\right)^\lambda - 1\right) / \lambda & \text{if } \lambda \neq 0 \text{ and } x_i - x_0 \geq 0\\
\log\left[1 + \frac{x_i - x_0}{s}\right] & \text{if } \lambda = 0 \text{ and } x_i - x_0 \geq 0\\
-\left( \left( 1 - \frac{x_i - x_0}{s}\right)^{2 - \lambda} - 1 \right) / \left(2 - \lambda \right) & \text{if } \lambda \neq 2 \text{ and } x_i - x_0 < 0\\
-\log\left[1 - \frac{x_i - x_0}{s}\right] & \text{if } \lambda = 2 \text{ and } x_i - x_0 < 0
\end{cases}
\end{equation}
```

The parameters of these power transformations can be optimised based by maximising the log-likelihood function, under the assumption that the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$ follows a normal distribution.
The log-likelihood functions for conventional Box-Cox and Yeo-Johnson transformations are well-known.
However, the introduction of scaling parameter $s$ prevents their direct use.
Here, we first derive the general form of the log-likelihood functions, and then derive their power-transformation specific definitions.

Let $f(x_1, \ldots, x_n)$ be the probability density function of feature $\mathbf{X} = \{ x_1, \ldots, x_n\}$, 
and $f^{\lambda, x_0, s} (\phi^{\lambda, x_0, s}(x_1), \ldots, \phi^{\lambda, x_0, s}(x_n))$ be the probability density function of 
the transformed feature $\phi^{\lambda, x_0, s} (\mathbf{X})$, that is assumed to follow a normal distribution.

The two probability density functions are related as follows:

```{=latex}
\begin{equation}
f^{\lambda, x_0, s}(x_1, \ldots, x_n) = f^{\lambda, x_0, s} (\phi^{\lambda, x_0, s}(x_1), \ldots, \phi^{\lambda, x_0, s}(x_n)) \left|\mathbf{J}\right|
\end{equation}
```
Where, $\left|\mathbf{J}\right|$ is the determinant of Jacobian $\mathbf{J}$.
The Jacobian takes the following form, with off-diagonal elements $0$:
```{=latex}
\begin{equation}
\mathbf{J} =
\begin{bmatrix}
    \frac{\partial}{\partial x_1} \phi^{\lambda, x_0, s}(x_1) & 0 & \dots & 0 \\
    0 & \frac{\partial}{\partial x_2} \phi^{\lambda, x_0, s}(x_2) & \dots & 0 \\
    \vdots & \vdots  & \ddots &  \vdots \\
    0  & 0 & 0 & \frac{\partial}{\partial x_n} \phi^{\lambda, x_0, s}(x_n)
\end{bmatrix}
\end{equation}
```

Thus, $\left| \mathbf{J} \right| = \prod_{i=1}^n \frac{\partial}{\partial x_i} \phi^{\lambda, x_0, s}(x_i)$.

Since in our situation $\{x_1, \ldots, x_n\}$ in $f^{\lambda, x_0, s}(x_1, \ldots, x_n)$ are considered fixed (i.e., known), $f^{\lambda, x_0, s}(x_1, \ldots, x_n)$ may be considered a likelihood function.
The log-likelihood function $\mathcal{l}^{\lambda, x_0, s}$ is then:
```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}^{\lambda, x_0, s} & = \log f^{\lambda, x_0, s}(x_1, \ldots, x_n) \\
 & = \log \left[ f^{\lambda, x_0, s} (\phi^{\lambda, x_0, s}(x_1), \ldots, \phi^{\lambda, x_0, s}(x_n)) \right] + \log \left|\mathbf{J}\right| \\
 & = \log \left[ f^{\lambda, x_0, s} (\phi^{\lambda, x_0, s}(x_1), \ldots, \phi^{\lambda, x_0, s}(x_n)) \right] + \log \prod_{i=1}^n \frac{\partial}{\partial x_i} \phi^{\lambda, x_0, s}(x_i) \\
 & = -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 + \sum_{i=1}^n \log \left[ \frac{\partial}{\partial x_i} \phi^{\lambda, x_0, s}(x_i)\right]
\end{split}
\end{equation}
```
With $\mu$ the average of $\phi^{\lambda, x_0, s}(\mathbf{X})$ and $\sigma^2$ its variance.
The first two terms derive directly from the log-likelihood function of a normal distribution, and are not specific to the type of power transformation used.
However, the final term differs between Box-Cox and Yeo-Johnson transformations.

## Box-Cox transformation

For the Box-Cox transformation the partial derivative is:
```{=latex}
\begin{equation}
\begin{split}
\frac{\partial}{\partial x_i} \phi_{\text{BC}}^{\lambda, x_0, s}(x_i) & = \frac{1}{s} \left(\frac{x_i - x_0}{s} \right)^{\lambda-1} \\
 & = \frac{1} {s^\lambda} \left(x_i - x_0 \right)^{\lambda - 1}
\end{split}
\end{equation}
```

Thus the final term in $\mathcal{l}_{\text{BC}}^{\lambda, x_0, s}$ is:
```{=latex}
\begin{equation}
\begin{split}
\sum_{i=1}^n \log \frac{\partial}{\partial x_i} \phi_{\text{BC}}^{\lambda, x_0, s}(x_i) & = \sum_{i=1}^n \log \left[ s^{-\lambda} (x_i - x_0)^{\lambda - 1} \right] \\
& = \sum_{i=1}^n \log \left[s^{-\lambda} \right] + \log \left[ (x_i - x_0)^{\lambda - 1} \right]\\
& = -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```

This leads to the following log-likelihood for the Box-Cox transformation:
```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{BC}}^{\lambda, x_0, s} = & -\frac{n}{2} \log \left[2 \pi \sigma^2 \right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& -n \lambda \log s + \left( \lambda - 1 \right) \sum_{i=1}^n \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```

We introduced per-sample weights $w_i$ to facilitate robust power transformations. The log likelihood of the robust Box-Cox transformation is:
```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{rBC}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \lambda \left( \sum_{i=1}^n w_i \right) \log s + \left( \lambda - 1 \right) \sum_{i=1}^n w_i \log \left[ x_i - x_0 \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Box-Cox transformed feature $\phi_{\text{BC}}^{\lambda, x_0, s} (\mathbf{X})$, respectively:

## Yeo-Johnson transformation

For the Yeo-Johnson transformation, the partial derivative is:
```{=latex}
\begin{equation}
\frac{\partial}{\partial x_i} \phi_{\text{YJ}}^{\lambda, x_0, s}(x_i) =
\begin{cases}
\frac{1}{s} \left(1 + \frac{x_i - x_0}{s}\right)^{\lambda - 1} & \text{if } x_i - x_0 \geq 0\\
\frac{1}{s} \left(1 - \frac{x_i - x_0}{s}\right)^{1 - \lambda} & \text{if } x_i - x_0 < 0
\end{cases}
\end{equation}
```

Thus the final term in $\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s}$ is:
```{=latex}
\begin{equation}
\begin{split}
\sum_{i=1}^n \log \frac{\partial}{\partial x_i} \phi_{\text{YJ}}^{\lambda, x_0, s}(x_i) & = - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```

This lead to the following log-likelihood for the Yeo-Johnson transformation:
```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{YJ}}^{\lambda, x_0, s} = & -\frac{n}{2} \log\left[2 \pi \sigma^2\right] -\frac{1}{2 \sigma^2} \sum_{i=1}^n \left( \phi^{\lambda, x_0, s}(x_i) - \mu \right)^2 \\
& - n \log s + (\lambda - 1) \sum_{i=1}^n \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```

The log likelihood of the robust Yeo-Johnson transformation is:
```{=latex}
\begin{equation}
\begin{split}
\mathcal{l}_{\text{rYJ}}^{\lambda, x_0, s} = & -\frac{1}{2} \left(\sum_{i=1}^n w_i \right) \log \left[ 2 \pi \sigma_w^2 \right] -\frac{1}{2 \sigma_w^2} \sum_{i=1}^n w_i \left( \phi^{\lambda, x_0, s}(x_i) - \mu_w \right)^2 \\
& - \left( \sum_{i=1}^n w_i \right) \log s + (\lambda - 1) \sum_{i=1}^n w_i \sgn(x_i - x_0) \log \left[1 + \frac{|x_i - x_0|}{s} \right]
\end{split}
\end{equation}
```
where $\mu_w$ and $\sigma^2_w$ are the weighted mean and weighted variance of the Yeo-Johnson transformed feature $\phi_{\text{YJ}}^{\lambda, x_0, s} (\mathbf{X})$:

# Appendix B: Optimisation of transformation parameters

Maximum likelihood estimation (MLE) is commonly used to optimise parameters for power transformation. Generally, optimisation requires minimisation or maximisation of a criterion. In MLE, the maximised criterion is the log-likelihood function of the normal distribution. Here, we investigate power transformation using optimisation criteria that are closely related to test statistics for normality tests.

Let $\mathbf{X}$ be a feature with ordered feature values, and $\mathbf{Y}^\lambda =\psi^{\lambda} \left(\mathbf{X} \right)$ and $\mathbf{Y}^{\lambda, x_0} =\psi^{\lambda, x_0} \left(\mathbf{X} \right)$ its transformed values using conventional and shift and scale invariant power transformations, respectively. Since power transformations are monotonic, $\mathbf{Y}$ will likewise be ordered.

Below we will focus on criteria based on the empirical density function and those based on skewness and kurtosis of the transformed featured. Other potential criteria, such as the Shapiro-Wilk test statistic [@Shapiro1965-zd] are not investigated here. In the case of the Shapiro-Wilk test statistic this is because of lack of scalability to features with many ($> 5000$) instances, and because adapting the test statistic to include weights is not straightforward.

## Empirical density function-based criteria

The first class of criteria is based on the empirical distribution function (EDF). Transformation parameters are then fit through minimisation of the distance between the empirical distribution function $F_{\epsilon}$ and the cumulative density function (CDF) of the normal distribution $F_{\mathcal{N}}$. Let $F_{\epsilon}\left(x_i \right) = \frac{i - 1/3}{n + 1/3}$ be the empirical probability of instance $i$. The normal distribution is parametrised by location parameter $\mu$ and scale parameter $\sigma$, both of which have to be estimated from the data. For non-robust power transformation, $\mu$ and $\sigma$ are sample mean and sample standard deviation, respectively. For robust power transformations, we estimate $\mu$ and $\sigma$ as Huber M-estimates of location and scale of the transformed feature $\phi^{\lambda, x_0} (\mathbf{X})$ [@Huber1981-su].

### Anderson-Darling criterion

The Anderson-Darling criterion is based on the empirical distribution function of $\mathbf{X}$. We define this criterion as follows:

```{=latex}
\begin{equation}
U_{\text{AD}} \left(\mathbf{X}, \lambda, x_0 \right) = \frac{1}{\sum_{i=1}^n w_i} \sum_{i=1}^n w_i \frac{\left( F_{\epsilon}\left(x_i \right) - F_{\mathcal{N}} \left(\psi^{\lambda, x_0} \left(x_i \right); \mu, \sigma \right) \right)^2} {F_{\mathcal{N}} \left(\psi^{\lambda, x_0} \left(x_i \right); \mu, \sigma \right) \left(1 - F_{\mathcal{N}} \left(\psi^{\lambda, x_0} \left(x_i \right); \mu, \sigma \right) \right) }
\end{equation}
```

Here $\mu$ and $\sigma$ are location and scale parameters as described above, and $w_i$ are weights as described in section **Insert**. For non-robust power transformations, all $w_i = 1$. Note that this criterion is not the same as the Anderson-Darling test statistic [@Anderson1952-gz], which involves solving (or approximating) an integral function, contains an extra scalar multiplication term, and does not include any extraneous weights $w_i$. The Anderson-Darling criterion seeks to minimise the squared Euclidean distance between the EDF and the normal CDF, with differences at the upper and lower end of the normal CDF receiving more weight than those at the the centre of the CDF.

### Cramér-von Mises criterion

The Cramér-von Mises criterion is also based on the empirical distribution function of $\mathbf{X}$. We define the Cramér-von Mises criterion as follows:
```{=latex}
\begin{equation}
U_{\text{CvM}} \left(\mathbf{X}, \lambda, x_0 \right) = \frac{1}{\sum_{i=1}^n w_i} \sum_{i=1}^n w_i \left( F_{\epsilon}\left(x_i \right) - F_{\mathcal{N}} \left(\psi^{\lambda, x_0} \left(x_i \right); \mu, \sigma \right) \right)^2
\end{equation}
```

Here $\mu$ and $\sigma$ are location and scale parameters as described above, and $w_i$ are weights as described in section **Insert**. For non-robust power transformations, all $w_i = 1$. The criterion is similar to the Cramér-von Mises test statistic [@Cramer1928-rc, @Von_Mises1928-ef], aside from a additive scalar value and the introduction of extraneous weights. This criterion, like the Anderson-Darling criterion, seeks to minimise the squared Euclidean distance between the EDF and the normal CDF. Unlike the Anderson-Darling criterion, this criterion weights all instances equally.

For conventional power transformations with a fixed shift parameter, the transformation $\phi^{\lambda, x_0} (\mathbf{X})$ may be substituted by $\phi^{\lambda} (\mathbf{X})$ in the definition of the Cramér-von Mises criterion.

## Skewness-kurtosis-based criteria

The second class of criteria seeks to reduce skewness and (excess) kurtosis of the transformed feature $\mathbf{Y}$. We will first define the location $\mu$ and scale $\sigma$ of the the transformed as these are required for computing skewness and kurtosis. Here, $\mu$ is defined as:

```{=latex}
\begin{equation}
\mu = \frac{\sum_{i=1}^n \phi^{\lambda, x_0} \left(x_i \right)} {\sum_{i=1}^n w_i}
\end{equation}
```

The location, or mean, is weighted using weights $w_i$, as described in section **Insert**. For non-robust transformations, $w_i = 1$. Then, $sigma^2$ is defined as:
```{=latex}
\begin{equation}
\sigma^2 = \frac{\sum_{i=1}^n w_i \left(\phi^{\lambda, x_0} \left( x_i \right) - \mu \right)^2}{\sum_{i=1}^n w_i}
\end{equation}
```

Skewness is defined as:
```{=latex}
\begin{equation}
s = \frac{\sum_{i=1}^n w_i \left(\phi^{\lambda, x_0} \left( x_i \right) - \mu \right)^3}{\sigma^3 \sum_{i=1}^n w_i}
\end{equation}
```

Kurtosis is defined as:
```{=latex}
\begin{equation}
k = \frac{\sum_{i=1}^n w_i \left(\phi^{\lambda, x_0} \left( x_i \right) - \mu \right)^4}{\sigma^4 \sum_{i=1}^n w_i}
\end{equation}
```

### D'Agostino criterion

The D'Agostino criterion defined here follows the D'Agostino $K^2$ test statistic [@DAgostino1990-kp]. This test statistic is composed of two separate test statistics, one of which is related to skewness, and the other to kurtosis. Both test statistics are computed in several steps. Let us first define $\nu=\sum_{i=1}^n w_i$. Thus for non-robust power transformations, $\nu = n$.

For the skewness test statistic we first compute [@DAgostino1990-kp]:

```{=latex}
\begin{equation}
\beta_1 = s \sqrt{ \frac{\left(\nu + 1\right) \left(\nu + 3\right)} {6 \left(\nu - 2\right)} }
\end{equation}

\begin{equation}
\beta_2 = 3 \frac{\left(\nu^2 + 27\nu - 70\right) \left(\nu + 1\right) \left(\nu + 3\right)} {\left(\nu - 2\right) \left(\nu + 5\right) \left(\nu + 7\right) \left(\nu + 9\right)}
\end{equation}

\begin{equation}
\alpha = \sqrt{\frac{2} {\sqrt{2 \beta_2 - 2} - 2}}
\end{equation}

\begin{equation}
\delta = \frac{1}{\sqrt{\log \left[\sqrt{-1 + \sqrt{2 * \beta_2 - 2}} \right]}}
\end{equation}
```

The skewness test statistic is then:

```{=latex}
\begin{equation}
Z_s = \delta \log\left[\frac{\beta_1}{\alpha} + \sqrt{\frac{\beta_1^2}{\alpha^2} + 1} \right]
\end{equation}
```

For the kurtosis test statistic we first compute [@DAgostino1990-kp, @Anscombe1983-nz]:

```{=latex}
\begin{equation}
\beta_1 = 3 \frac{\nu - 1}{\nu + 1}
\end{equation}

\begin{equation}
\beta_2 = 24 \nu \frac{\left(\nu - 2\right)\left(\nu - 3\right)}{\left(\nu + 1\right)^2 \left(\nu + 3\right) \left(\nu + 5\right)}
\end{equation}

\begin{equation}
\beta_3 = 6 \frac{\nu^2 - 5 \nu + 2}{\left(\nu + 7\right) \left(\nu + 9\right)} \sqrt{6 \frac{\left(\nu + 3\right) \left(\nu + 5\right)}{\nu \left(\nu - 2\right) \left(\nu - 3 \right)}}
\end{equation}

\begin{equation}
\alpha_1 = 6 + \frac{8}{\beta_3} \left[\frac{2}{\beta_3} + \sqrt{1 + \frac{4}{\beta_3^2}} \right]
\end{equation}

\begin{equation}
\alpha_2 = \frac{k - \beta_1}{\sqrt{\beta_2}}
\end{equation}
```

The kurtosis test statistic is then:

```{=latex}
\begin{equation}
Z_k = \sqrt{\frac{9 \alpha_1}{2}} \left[ 1 - \frac{2}{9 \alpha_1} - \left(\frac{1 - 2 / \alpha_1}{1 + \alpha_2 \sqrt{2 / \left(\alpha_1 - 4 \right)}} \right)^{1 / 3}  \right]
\end{equation}
```

The D'Agostino $K^2$ test statistic and our criterion are the same, and are defined as:
```{=latex}
\begin{equation}
U_{\text{DA}} \left(\mathbf{X}, \lambda, x_0 \right) = Z_s^2 + Z_k^2
\end{equation}
```

The main difference between the test statistic as originally formulated, and the criterion proposed here is the presence of weights for robust power transformation.

### Jarque-Bera criterion

The second criterion based on skewness and kurtosis is the Jarque-Bera criterion. It is relatively simple to compute, compared to the D'Agostino criterion:
```{=latex}
\begin{equation}
U_{\text{JB}} \left(\mathbf{X}, \lambda, x_0 \right) = s^2 + \left(k - 3\right)^2 / 4
\end{equation}
```

The main difference between the above criterion and the Jarque-Bera test statistic [@Jarque1980-hw] is that a scalar multiplication is absent.

## Optimisation using non-MLE criteria

Each of the criteria described in the previous section can be used for optimisation, i.e.:

```{=latex}
\begin{equation}
\left\{ \hat{\lambda}, \hat{x}_0 \right\} = \argmin_{\lambda, x_0} U\left(\mathbf{X}, \lambda, x_0 \right)
\end{equation}
```

For conventional power transformations with a fixed shift parameter, the transformation $\phi^{\lambda, x_0} (\mathbf{X})$ may be substituted by $\phi^{\lambda} (\mathbf{X})$, or equivalently, $x_0$ is fixed:
```{=latex}
\begin{equation}
\left\{ \hat{\lambda}\right\} = \argmin_{\lambda} U\left(\mathbf{X}, \lambda; x_0 \right)
\end{equation}
```

# Appendix B: Simulations with other optimisation criteria

```{r shifted-distributions-other-criteria, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Shift-sensitive power transformation produces transformation parameters that are invariant to location. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively,  which then underwent a shift $d$. ",
  "Estimates of transformation parameter $\\lambda$ with the original power transformations (circle) show strong dependency on the overall location of the distribution, ",
  "whereas estimates with the shift-sensitive power transformations (triangle) are constant.")

  .plot_shifted_distributions_other_criteria(manuscript_dir = manuscript_dir, plot_theme = plot_theme)
```

>>>>

In this section we simulate data to assess invariance to location and scale of the proposed power transformations, weighting for robust transformations, and to develop the empirical central normality test.
The $\lambda$ parameter for conventional power transformations (Eqn. \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}) and $\lambda$, $x_0$ and $s$ parameters for location and scale invariant power transformations (Eqn. \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) are estimated using the BOBYQA algorithm for derivative-free bound constraint optimisation [@Powell2009-zb] through maximum likelihood estimation. Appendix B describes other criteria, and Appendix C the results of simulations using these criteria.

@@

To assess whether the proposed power transformations lead to $\lambda$ values that are invariant to location and scale of the distribution, we simulate three different distributions. The first distribution is a normal distribution, as previously shown in Figure \ref{fig:decreased-normality}.
We first randomly draw $10000$ values from a normal distribution: $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{N}\left(0, 1\right)$, or equivalently $\mathbf{X}_{\text{normal}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.5, 2\right)$.
The second distribution is a right-skewed normal distribution $\mathbf{X}_{\text{right}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.2, 2\right)$.
The third distribution is a left-skewed normal distribution $\mathbf{X}_{\text{left}} = \left\{x_1, x_2, \ldots, x_{10000} \right\} \sim \mathcal{AGN}\left(0, 1/\sqrt{2}, 0.8, 2\right)$.
We then compute transformation parameter $\hat{\lambda}$ using the original definitions (equations \ref{eqn:box-cox-original} and \ref{eqn:yeo-johnson-original}) and the location and scale invariant definitions (equations \ref{eqn:box-cox-invariant} and \ref{eqn:yeo-johnson-invariant}) for each distribution.
To assess location invariance, a positive value $d_{\text{shift}}$ is added to each distribution with $d_{\text{shift}} \in [1, 10^6]$. Similarly, to assess scale invariance, each distribution is multiplied by a positive value $d_{\text{scale}}$, where $d_{\text{scale}} \in [1, 10^6]$.

```{r shifted-distributions, warning=FALSE, message=FALSE, fig.cap=cap}
cap <- paste0(
  "Invariant power transformation produces transformation parameters that are invariant to location and shape. ",
  "Samples were drawn from normal, right-skewed and left-skewed distributions, respectively, which then underwent a shift $d_{\\text{shift}}$ or multiplication by $d_{\\text{scale}}$. ",
  "Estimates of transformation parameter $\\lambda$ with the conventional power transformations (circle) show strong dependency on the overall location and scale of the distribution, ",
  "whereas estimates with the invariant power transformations (triangle) are constant."
)

@@
